---
title: "Muley, Tushar Assignment 1-2 Week 1"
output:
  word_document: default
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
date: "June 13, 2021"
---

# 1. Import, Plot, Summarize, and Save Data
# Using the Bureau of Labor Statistics data, choose a dataset that interest you. 
# Then generate summary statistics for 2 variables, plot some of the features 
# (e.g., histograms, box plots, density plots, etc.) of several variables, and save the 
# data locally as CSV files.

#Imported Financial_activities_all_states_us.csv
#variable to shorting name


```{r}

fin_act <- read.csv('C:/Users/Tushar/RStudioProjects/DSC630_SUMMER_2021/financial_activities_all_states_us.csv')

```
#Install pastecs package
```{r}
install.packages("pastecs",repos = "http://cran.us.r-project.org")
library(pastecs,)

```

```{r}
#See the column headers
head(fin_act,)
```

```{r}
#Summary Statistics for 2 variables
attach(fin_act)
sum_fin_act<-cbind(month1_emplvl, total_qtrly_wages)
stat.desc(sum_fin_act)
```

#Plot some of the features 
# (e.g., histograms, box plots, density plots, etc.) of several variables

```{r}
#Move data into a dataframe
fin_act_df<-data.frame(fin_act)

#Preview the dataframe
head(fin_act_df)


```


```{r}
library(ggplot2)
# Basic histogram of average week wages
ggplot(fin_act_df, aes(x=avg_wkly_wage)) + geom_histogram(binwidth = 100)
```



```{r}
#Denisty Plot of average weekly wages
ggplot(fin_act_df, aes(x=avg_wkly_wage)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)
```

```{r}
#Historam of average 
ggplot(fin_act_df, aes(x=lq_avg_wkly_wage)) + geom_histogram()
```

```{r}
#Historam of quarterly contributions
ggplot(fin_act_df, aes(x=qtrly_contributions)) + geom_histogram(binwidth = 10000000000)
```

```{r}
#Denisty Plot of quarterly contributions
ggplot(fin_act_df, aes(x=qtrly_contributions)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)
```

```{r}

#Denisty Plot of average weekly wages
ggplot(fin_act_df, aes(x=lq_qtrly_estabs)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)


```

#Need to filter the data by a level code. 
#Level code 53 	Statewide, by Supersector -- by ownership sector

```{r}

head(fin_act_df)
```


```{r}

fin_act_C53_df <- fin_act_df[fin_act_df$agglvl_code == '53',]



```
```{r}
head(fin_act_C53_df)
```

```{r}
#Min
min(fin_act_C53_df$total_qtrly_wages)

```

```{r}
#Max
max(fin_act_C53_df$total_qtrly_wages)
```

```{r}
#Median
median(fin_act_C53_df$total_qtrly_wages)
```

```{r}
#Mean
mean(fin_act_C53_df$total_qtrly_wages)
```

```{r}
#Median
median(fin_act_C53_df$avg_wkly_wage)
```


```{r}
#Denisty Plot of qtrly_establishment
ggplot(fin_act_C53_df, aes(x=qtrly_estabs)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)
```

```{r}
#Histogram of month2_emplvl
ggplot(fin_act_C53_df, aes(x=month2_emplvl)) + geom_histogram(binwidth = 100000)
```


```{r}
#Density plot of oty_month1_emplvl_chg
ggplot(fin_act_C53_df, aes(x=oty_month1_emplvl_chg)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)
```


```{r}
#Boxplot of month 3 Employment and own code
ggplot(fin_act_C53_df, aes(x=month3_emplvl, y=own_code, group=own_code)) + 
    geom_boxplot() + facet_wrap(~own_code)

```


```{r}
#Bar graph of own codes
ggplot(fin_act_C53_df) +
  geom_bar(mapping = aes(x = own_code))

```

#2. Explore Some Bivariate Relations
#Use the same dataset within the same website to explore some bivariate relations #(e.g. bivariate plot, correlation, table cross table etc.)


```{r}

install.packages("ggpubr", repos = "http://cran.us.r-project.org")
library("ggpubr")
```

#Checking to see Quarterly wage correlate to Taxable Quarter Wages

```{r}
ggscatter(fin_act_C53_df, x = "total_qtrly_wages", y = "taxable_qtrly_wages", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Total Quarterly Wages", ylab = "Taxable Quarterly Wages")
```

#QQPlot

```{r}
# total_qtrly_wages
ggqqplot(fin_act_C53_df$total_qtrly_wages, ylab = "total_qtrly_wages")

# Taxable Quarterly Wages
ggqqplot(fin_act_C53_df$taxable_qtrly_wages, ylab = "taxable_qtrly_wages")
```

#Pearson Correlation
```{r}
person_cor <- cor.test(fin_act_C53_df$total_qtrly_wages, 
                fin_act_C53_df$taxable_qtrly_wages, method = "pearson")
person_cor
```

#Pearson Correlation:

#t is the t-test statistic value (t = 13.168),
#df is the degrees of freedom (df= 190),
#p-value is p-value = 2.2e^-16}).
conf.int is the confidence interval of the correlation coefficient at 95% 
(conf.int = [0.6087, 0.7582]);

sample estimates is the correlation coefficient (Cor.coeff = 0.6907).



#Kendall Rank Correlation
```{r}
kendall_cor <- cor.test(fin_act_C53_df$total_qtrly_wages, 
                fin_act_C53_df$taxable_qtrly_wages,  method="kendall")
kendall_cor
```

#Kendall Correlation:
#Correlation coeffient between total quarterly wages and taxable quarterly wages
#0.6706 and p-value = 2.2e^-16


#Spearman Correlation
```{r}
spreaman_cor <-cor.test(fin_act_C53_df$total_qtrly_wages, 
                fin_act_C53_df$taxable_qtrly_wages,  method = "spearman")
spreaman_cor
```

#Spearman Correlation:
#Correlation coefficient between quarterly wages and taxable quarterly wages is 
#0.8049 rho and p-value is 2.2e^-16

#Based on this these correlation I would say we have a positive correlation between #quarterly wages and taxable quarterly wages. 

#It is on a perfect correlation but strong positive correlation:
#Pearson: 0.6907
#Kendall: 0.6706
#Spearan: 0.8049

#If quarter wages go up so does taxable quarterly wages.


#3. Organize a Data Report
#Generate a summary report. Make sure to include: summary for every variable, #structure and type of data elements, discuss four results of your data.

```{r}
str(fin_act_C53_df)
```






